---
title: "CRI_Replication_Git"
author: "Rebecca"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required Packages
```{r echo=T, results='hide', message=FALSE, warning=FALSE, include=FALSE}
require(tidyverse)
require(summarytools)
require(pastecs)
require(skimr)
require(Hmisc)
require(rstatix)
require(car)
require(gmodels)
require(ggpubr)
require(RColorBrewer)
require(scales)
require(ggimage)
```

#Session Paramters
```{r}
options(scipen=999)
```

# Import Data
```{r echo=F}
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRXlLy7vNXNWyB3OuxRtPWCdqo056Piu17E9x9QP0lVs33NVuZl3YFnS6ToUyLKOpQ6kRu2ZFip-PpZ/pub?gid=0&single=true&output=csv"
dat <- read.csv(url, header = TRUE)

dat <- dat[2:326,]


# Dataframe for only unique studies
dat_unique <- dat %>%
  filter(expt_num == 1)

```

# Descriptives
## Open Science
```{r}
freq(dat_unique$open_access)
freq(dat_unique$ethics)
freq(dat_unique$consent)
freq(dat_unique$prereg)
freq(dat_unique$disciplines_availability)

dat_consent <- dat_unique %>%
  filter(consent == 1 & ethics == 0)

freq(dat_unique$discipline1_CODED)

dat_discipline <- dat_unique %>%
  dplyr::select(discipline1_CODED:discipline4_CODED)

discipline_tab <- as.data.frame(table(unlist(dat_discipline)))


freq(dat_unique$open_materials)
freq(dat_unique$open_measures)
freq(dat_unique$open_code)
freq(dat_unique$code_repository)
freq(dat_unique$open_materials)
freq(dat_unique$open_data)
freq(dat_unique$study_repository)
```

## Population
```{r}
freq(dat_unique$application_CODED)
freq(dat_unique$population)
freq(dat_unique$country_CODED)
```


### Sample Size
```{r}
dat$N_CODED <- as.numeric(dat$N_CODED)

freq(dat$N_CODED)

skim(dat$mean_age_CODED)
stat.desc(dat$mean_age_CODED)


skim(dat$N_CODED)
stat.desc(dat$N_CODED)

freq(dat$age_gender_after_exclusion)

dat_gender <- dat %>%
  dplyr::select(female_reported_CODED, male_reported_CODED, non_binary_reported_CODED, not_specified_reported_CODED) %>% 
  replace(. == "N.R.", NA)

dat_gender <- sapply(dat_gender, as.numeric)
dat_gender <- as.data.frame(dat_gender)

proportions <- colSums(dat_gender, na.rm = T) / sum(dat_gender, na.rm = T)
proportions

dat_mf <- dat_gender %>%
  filter(non_binary_reported_CODED == 0 & not_specified_reported_CODED == 0)

dat_mf$prop <- dat_mf$male_reported_CODED / (dat_mf$male_reported_CODED + dat_mf$female_reported_CODED)
stat.desc(dat_mf$prop)

```



```{r}
dat$age_round <- round(dat$mean_age_CODED)

dat$min_age_round <- round(dat$min_age_CODED)
dat$max_age_round <- round(dat$max_age_CODED)


# Filter out rows with non-numeric values in min_age and max_age columns
dat_age <- dat %>%
  filter(!is.na(as.numeric(min_age_round)) & !is.na(as.numeric(max_age_round))) %>%
  mutate(min_age = as.numeric(min_age_round), max_age = as.numeric(max_age_round)) %>%
  dplyr::select(ID, expt_num, mean_age_CODED, min_age_round, max_age_round) %>%
  mutate(ID_unique = paste0(ID, "_", expt_num))

# Create a sequence of ages from min_age to max_age for each row
dat_age_TOTAL <- dat_age %>%
  mutate(ages = map2(min_age_round, max_age_round, ~seq(.x, .y, by = 1))) %>%
  unnest(ages)

# Count the occurrences of each age
result <- dat_age_TOTAL %>%
  count(ages)

# Rename the columns
result <- result %>%
  rename(age = ages, count = n)

result$percent <- round(100 * result$count / sum(result$count), 2)

# Create histogram
gg_age <- ggplot(result, aes(x = age, y = percent)) +
  geom_bar(stat = "identity", fill = "#2166AC", colour = "black", width = 1) +
  labs(x = "Age", y = "Percntage of studies with this age") +
  ylim(0, 12) +
    theme(
        panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face = "bold", size = 9),
        axis.title.y = element_text(face = "bold", size = 9))

gg_age

ggsave("gg_age.pdf", height = 5)
```



## Robots / Interaction
```{r}
freq(dat$robot_number)

freq(dat$operation_CODED)

dat_operation <- dat %>%
  separate_rows(operation_CODED, sep = ",") %>%
  dplyr::select(operation_CODED) %>%
  mutate(operation_CODED = as.factor(operation_CODED))

freq(dat_operation$operation_CODED)

operation_counts <- table(dat_operation$operation_CODED)

operation_dat <- data.frame(operation_counts)
operation_dat$percent <- round(100 * operation_dat$Freq / sum(operation_dat$Freq), 2)

operation_dat$Var1 <- factor(operation_dat$Var1, levels = operation_dat$Var1[order(operation_dat$percent, decreasing = TRUE)])
```




```{r}
dat_robots <- dat %>%
  separate_rows(robot_model, sep = ",") %>%
  dplyr::select(robot_model)

robot_freq <- freq(dat_robots$robot_model)

value_counts <- dat_robots %>%
  count(robot_model)

# Identify values that appear only once
values_to_replace <- value_counts %>%
  filter(n <= 5) %>%
  pull(robot_model)

#Replace values that appear only once with "Other"
dat_robots <- dat_robots %>%
  mutate(robot_CODED = if_else(robot_model %in% values_to_replace, "Other", robot_model))

freq(dat_robots$robot_CODED)

robot_counts <- dat_robots %>%
  count(robot_CODED) %>%
  arrange(-n) %>%
  mutate(robot_CODED = factor(robot_CODED, levels = robot_CODED))
```
# Pie Graphs
## Pie Graph Functions
```{r}
create_counts_dataframe <- function(df, column_name) {
  # Create summary table with counts
  counts <- table(df[, column_name])
  dat_counts <- data.frame(counts)
  
  # Calculate percentages
  dat_counts$percent <- round(100 * dat_counts$Freq / sum(dat_counts$Freq), 2)
  
  # Order factor levels based on percentages
  dat_counts$Var1 <- factor(dat_counts$Var1, levels = dat_counts$Var1[order(dat_counts$percent, decreasing = TRUE)])
  
  return(dat_counts)
}
  
colour_mapping2 <- c("Reported" = "#F4A582",
                   "Not Reported" = "#B2182B")

colour_mapping3 <- c("Reported" = "#F4A582",
                   "Partially Reported" = "#D6604D",
                   "Not Reported" = "#B2182B")

display.brewer.all(8, type = "div", colorblindFriendly = TRUE)
display.brewer.pal(8, "RdBu")
brewer.pal(12, "RdBu")

rdbu_colours <- c("#67001F", "#B2182B", "#D6604D", "#F4A582", "#FDDBC7", "#F7F7F7", "#D1E5F0", "#92C5DE", "#4393C3", "#2166AC", "#053061", "#053061" )

other_color <- "grey"  
```


```{r}
create_pie_chart <- function(data, legend_label, nudge_label = 1, label_spacing = 0.25, colour_mapping, line_width = 1, text_size = 5, plot_title = NULL) {
  # Reorder the data based on the percentage in descending order
  data <- data[order(-data$percent), ]

  # Create a custom color palette with the specified mapping
  custom_palette <- colour_mapping[match(data[[1]], names(colour_mapping))]

  data |>
    transmute(
      Var1 = factor(.data[[1]], levels = unique(.data[[1]])),  # Maintain the desired order of levels
      percent,
      cuml_pct = cumsum(percent)
    ) |>
    ggplot(aes(x = 0, y = percent, fill = Var1)) +
    geom_col(width = 1) +
    coord_polar(theta = "y") +
    labs(fill = legend_label, title = plot_title) +
    scale_fill_manual(values = custom_palette, breaks = unique(Var1)) +
    geom_segment(
      aes(
        y = cuml_pct - percent / 2,
        yend = cuml_pct - percent / 2,
        x = 0.2,
        xend = nudge_label * (1 - label_spacing)
      ),
      size = line_width
    ) +
    geom_text(
      aes(y = cuml_pct - percent / 2, label = paste0(percent, "%")),
      nudge_x = nudge_label,
      size = text_size
    ) +
    theme_void() +
    theme(
      legend.title = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, margin = margin(b = 0))
    )
}

```


```{r}
create_bar_graph <- function(data, right_var, other_color, x_label, y_label, legend_title) {
  data$Var1 <- factor(data$Var1, levels = levels(data$Var1))
  
  right_category <- data %>% filter(Var1 == right_var)
  
  # Remove the right variable category from the main data frame
  data <- data %>% filter(Var1 != right_var) %>%
    mutate(Var1 = fct_reorder(Var1, desc(percent)))
  
  custom_percent_label <- function(labels) {
    paste0(labels, "%")
  }
  
  # Filter out categories with zero frequency or percentage
  data <- data %>% filter(percent != 0)
  
  # Determine the number of categories and colors
  n_colors <- length(levels(data$Var1))
  max_n <- 11  # Maximum number of colors in the palette
  
  # Create the color palette with repeating "RdBu" colors for left categories
  colors <- rep_len(brewer.pal(n = max_n, name = "RdBu"), n_colors)
  
  # Map the right variable category to "other color"
  colors[n_colors] <- other_color
  
  ggplot(data, aes(x = Var1, y = percent, fill = Var1)) +
    geom_bar(stat = "identity", width = 0.9) +
    labs(x = x_label, y = y_label, fill = legend_title) +
    theme(
      panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
      panel.background = element_rect(fill = "white"),
      axis.title.x = element_text(face = "bold", size = 9),
      axis.title.y = element_text(face = "bold", size = 9),
      legend.title = element_text(face = "bold", size = 9)
    ) +
    # Plot the right variable column with increased spacing using position_nudge
    geom_col(data = right_category, aes(x = right_var, y = percent, fill = Var1), width = 0.9) +
    scale_fill_manual(values = colors,
                      breaks = levels(data$Var1),
                      labels = levels(data$Var1),
                      drop = TRUE) +  # Exclude categories with zero frequency/percentage from legend
    scale_x_discrete(limits = c(levels(data$Var1), right_var)) +
    scale_y_continuous(labels = custom_percent_label)
}

```

## Graphs Data
```{r}
dat_pies_unique <- dat_unique %>%
  mutate(country_CODED = if_else(country_CODED != "N.R.", "Reported", "Not Reported", country_CODED)) %>%
  mutate(mean_age_CODED = if_else(mean_age_CODED != "N.R.", "Reported", "Not Reported", mean_age_CODED)) %>%
  mutate(gender_reporting = if_else(gender_reporting != "N.R.", "Reported", "Not Reported", gender_reporting)) %>%
  mutate(disciplines_availability = dplyr::recode(disciplines_availability,
                           "0" = "Not Reported",
                           "0.5" = "Partially Reported",
                           "1" = "Reported")) %>% 
  mutate(disciplines_availability = factor(disciplines_availability, levels = c("Not Reported", "Partially Reported", "Reported"))) %>%
  mutate(across(starts_with("open_"), ~ dplyr::recode(., "0.5" = "Partially Available",
                                               "0" = "Not Available",
                                               "1" = "Available",
                                               "N.A." = "Not Applicable",
                                               "UpnReq" = "Upon Request")))  %>%
    mutate(ethics = dplyr::recode(ethics,
                           "0" = "Not Reported",
                           "1" = "Reported")) %>% 
    mutate(consent = dplyr::recode(consent,
                           "0" = "Not Reported",
                           "1" = "Reported")) %>% 
    mutate(prereg = dplyr::recode(prereg,
                           "0" = "Not Pre-Registered",
                           "1" = "Pre-Registered"))

levels(dat_pies_unique$disciplines_availability)

dat_pies <- dat %>%
  mutate(mean_age_CODED = if_else(mean_age_CODED != "N.R.", "Reported", "Not Reported", mean_age_CODED)) %>%
  mutate(gender_reporting = if_else(gender_reporting != "N.R.", "Reported", "Not Reported", gender_reporting)) %>%
  mutate(N_CODED = if_else(N_CODED != "N.R.", "Reported", "Not Reported", N_CODED)) %>%
  mutate(robot_CODED = if_else(robot_CODED != "N.R.", "Reported", "Not Reported", robot_CODED)) %>%
  mutate(robot_interaction = if_else(robot_interaction != "N.R.", "Reported", "Not Reported", robot_interaction)) %>%
  mutate(length_CODED = if_else(length_CODED != "0", "Reported", "Not Reported", length_CODED)) %>%
  mutate(number_coded = dplyr::recode(number_coded, "M" = "Multiple", "S" = "Single", "N.R." = "Not Reported")) %>%
  mutate(operation_CODED = if_else(operation_CODED != "N.R.", "Reported", "Not Reported", operation_CODED))

```



### Countries
```{r}
gg_country <- create_counts_dataframe(dat_pies_unique, "country_CODED")

gg_country_p <- create_pie_chart(
  gg_country, 
  "Country", nudge_label = 0.8, label_spacing = 0.2,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Country")

gg_country_p
```

### Disciplines 
```{r} 
gg_disciplines <- create_counts_dataframe(dat_pies_unique, "disciplines_availability") %>%
  mutate(Var1 = factor(Var1, levels = c("Reported", "Partially Reported", "Not Reported")))

gg_disciplines_p <- create_pie_chart(
  gg_disciplines, 
  "Disciplines", nudge_label = 1.1, label_spacing = 0.35,
  colour_mapping = colour_mapping3, line_width = 1, text_size = 5, plot_title = "Disciplines")

gg_disciplines_p

overview_pies <- ggarrange(gg_country_p, gg_disciplines_p, ncol=2, widths = c(1, 1.5))

overview_pies

ggsave("overview_pies.pdf", width = 17)
```

```{r}
gg_discipline1 <- create_counts_dataframe(dat_unique, "discipline1_CODED") %>%
   group_by(Var1) %>%
  mutate(Var1 = as.character(Var1)) %>%
  mutate(Var1 = ifelse(percent < 1, "Other", Var1)) %>%
  summarise(Freq = sum(Freq), percent = sum(percent)) %>%
 mutate(Var1 = fct_reorder(Var1, desc(percent)))

new_row <- data.frame(Var1 = "", Freq = 0, percent = 0)
gg_discipline1 <- rbind(gg_discipline1, new_row)

create_bar_graph(gg_discipline1, "N.R.", "grey","First Author Discipline", "Percentage of Total Papers", "Discipline") 

discipline_bar

scale_x_discrete(labels = c("Computer Science", "Psychology", "Engineering", "Education", "Medecine", "Communication", "Design", "Other","Art", "Humanities", "Literature", "N.R."))
  

ggsave("discipline_bar.pdf", width = 15)
```

```{r}
discipline_tab$percent <- round(100 * discipline_tab$Freq / sum(discipline_tab$Freq), 2)

discipline_tab <- discipline_tab[-1, ]

discipline_tab <- discipline_tab %>%
  group_by(Var1) %>%
  mutate(Var1 = as.character(Var1)) %>%
  mutate(Var1 = ifelse(percent < 1, "Other", Var1)) %>%
  summarise(Freq = sum(Freq), percent = sum(percent)) %>%
 mutate(Var1 = fct_reorder(Var1, desc(percent)))

discipline_tab <- rbind(discipline_tab, new_row)

create_bar_graph(discipline_tab, "N.R.", "grey", "Discipline", "Percentage of Total Papers", "Discipline")

ggsave("all_disciplines.pdf", width = 15)
```
### Application
```{r}
gg_application <- create_counts_dataframe(dat_pies_unique, "application_CODED")

ggplot(gg_application, aes(x = Var1, y = percent, fill = Var1)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "RdBu") +
  labs(x = "Application", y = "Percentage of Total Papers", fill = "Application") +
    theme(
        panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face = "bold", size = 9),
        axis.title.y = element_text(face = "bold", size = 9))

ggsave("application_bar.pdf", width = 15)
```

### Population
```{r}
gg_population <- create_counts_dataframe(dat_pies_unique, "population") %>%
  group_by(Var1) %>%
  mutate(Var1 = as.character(Var1)) %>%
  mutate(Var1 = ifelse(percent < 1, "Other", Var1)) %>%
  summarise(Freq = sum(Freq), percent = sum(percent)) %>%
 mutate(Var1 = fct_reorder(Var1, desc(percent)))

ggplot(gg_population, aes(x = Var1, y = percent, fill = Var1)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "RdBu") +
  scale_x_discrete(labels = c("Neurotypical", "ASD", "Mixed", "Other", "Multiple\nIrregularities", "Cerbral\nPalsy", "Cognitively\nImpaired")) +
  labs(x = "Population", y = "Percentage of Total Papers", fill = "Population") +
    theme(
        panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face = "bold", size = 9),
        axis.title.y = element_text(face = "bold", size = 9))


create_bar_graph(gg_population, "Other", "grey", "Population", "Percentage of Total Papers", "Population")

ggsave("population_bar.pdf", width = 15, height = 7)
```


### Gender
```{r}
gg_gender <- create_counts_dataframe(dat_pies, "gender_reporting")

freq(dat_pies$gender_reporting)

gg_gender_p <- create_pie_chart(
  gg_gender, 
  "Gender", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Gender")

gg_gender_p
```

#### Graph of Proportions
```{r}
counts_mf <- hist(dat_mf$prop, breaks = 20, plot = FALSE)$counts
total_mf <- sum(counts_mf)
percentages_mf <- counts_mf / total_mf * 100

ggplot(dat_mf, aes(x = prop)) +
  geom_histogram(aes(y = after_stat(count)/sum(after_stat(count))), 
                 fill = "#2166AC", colour = "black", bins = 20) +
  labs(x = "Proportion", y = "Percentage of Total Studies") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  scale_y_continuous(labels = scales::percent) +
  theme(
    panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
    panel.background = element_rect(fill = "white"),
    axis.title.x = element_text(face = "bold", size = 9),
    axis.title.y = element_text(face = "bold", size = 9)
  )

  

ggsave("gg_gender.pdf", height = 5)

```


### Age
```{r}
gg_age <- create_counts_dataframe(dat_pies, "mean_age_CODED")

gg_age_p <- create_pie_chart(
  gg_age, 
  "Reporting", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Age")

#theme(plot.title = element_text(hjust = 0.5, margin = margin(b = -85)))


gg_age_p

```

### Sample Size
```{r}
gg_sample <- create_counts_dataframe(dat_pies, "N_CODED")

gg_sample_p <- create_pie_chart(
  gg_sample, 
  "Sample Size", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Sample Size")

gg_sample_p


dat_pies_unique$N_CODED <- as.numeric(dat_pies_unique$N_CODED)

dat_sample <- dat_pies_unique %>%
  dplyr::filter(N_CODED <= 50)

ggplot(dat_pies_unique, aes(x = N_CODED)) +
  geom_histogram(aes(y = after_stat(count)/sum(after_stat(count))), 
                 fill = "#2166AC", colour = "black", bins = 50) +
  labs(x = "Sample Size", y = "Percentage of Total Studies (N = 325)") +
  scale_x_continuous(limits = c(1, 600), breaks = seq(0, 600, 50)) +
  scale_y_continuous(labels = scales::percent) +
   theme(
        panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face = "bold", size = 9),
        axis.title.y = element_text(face = "bold", size = 9))

ggsave("sample_sizes.pdf", width = 10)

dat_sample <- dat_pies_unique %>%
  dplyr::filter(N_CODED <= 100)

ggplot(dat_sample, aes(x = N_CODED)) +
  geom_histogram(aes(y = after_stat(count)/sum(after_stat(count))),
                 fill = "#2166AC", colour = "black", bins = 50) +
  labs(x = "Sample Size", y = "Percentage of Total Studies (N = 325)") +
  scale_x_continuous(limits = c(1, 100), breaks = seq(0, 100, 5)) +
  scale_y_continuous(labels = scales::percent) +
   theme(
        panel.grid.major = element_line(color = "#E5E5E5", linetype = "solid", linewidth = 0.3),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face = "bold", size = 9),
        axis.title.y = element_text(face = "bold", size = 9))

ggsave("sample_100.pdf", width = 10)
```

## Demographics
```{r}
demographic_pies <- ggarrange(gg_age_p, gg_gender_p, gg_sample_p, ncol=3, common.legend = TRUE, legend = "bottom", widths = c(1, 1, 1), align = "h")

demographic_pies

ggsave("demographic_pies.pdf", width = 17)
```

### Length / Number of Interaction(s)
```{r}
gg_length <- create_counts_dataframe(dat_pies, "length_CODED")
gg_length_p <- create_pie_chart(
  gg_length, 
  "Length of Interaction", nudge_label = 1, label_spacing = 0.3,
  colour_mapping = colour_mapping3, line_width = 1, text_size = 5, plot_title = "Length of Interactions")

colour_mapping_sessions <- c("Single" = "#F4A582",
                   "Multiple" = "#D6604D",
                   "Not Reported" = "#B2182B")

gg_number <- create_counts_dataframe(dat_pies, "number_coded") %>%
  mutate(Var1 = factor(Var1, (levels = c("Single", "Not Reported", "Multiple"))))

gg_number_p <- create_pie_chart(
  gg_number, 
  "Number of Interactions", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping_sessions, line_width = 1, text_size = 5, plot_title = "Number of Interactions")

interaction_pies <- ggarrange(gg_length_p, gg_number_p, ncol=2)

ggsave("interaction_pies.pdf", width = 15)
```



### Robots
```{r}
gg_robot_model <- create_counts_dataframe(dat_pies, "robot_CODED")
gg_robot_model_p <- create_pie_chart(
  gg_robot_model, 
  "Reporting", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Robot Model")

gg_robot_operation <- create_counts_dataframe(dat_pies, "operation_CODED")
gg_robot_operation_p <- create_pie_chart(
  gg_robot_operation, 
  "Robot Operation", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Robot Operation")

gg_robot_interaction <- create_counts_dataframe(dat_pies, "robot_interaction")
gg_robot_interaction_p <- create_pie_chart(
  gg_robot_interaction, 
  "Robot Operation", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Type of Interaction")

robot_pies <- ggarrange(gg_robot_model_p, gg_robot_operation_p, gg_robot_interaction_p, ncol=3, common.legend = TRUE, legend = "bottom")

robot_pies

ggsave("robot_pies.pdf", width = 17)
```

```{r}
robot_counts <- robot_counts %>%
   mutate(percentage = n / sum(n) * 100)

robot_counts$Var1 <- robot_counts$robot_CODED
robot_counts$percent <- robot_counts$percentage

robot_row <- data.frame(robot_CODED = "", n = 0, percentage = 0, Var1 = "", percent = 0)

robot_counts <- rbind(robot_counts, robot_row)

create_bar_graph(robot_counts, "N.R.", "grey", "Robot Model", "Percentage of Total Studies", "Robot Model") +
geom_image(data = data.frame(x = "Nao", y = 40, image = "full-nao.png"),
            aes(x = x, y = y, image = image, size = 0.15), inherit.aes = FALSE) +
geom_image(data = data.frame(x = "Pepper", y = 12, image = "pepper.png"),
            aes(x = x, y = y, image = image, size = 0.15), inherit.aes = FALSE) +
  geom_image(data = data.frame(x = "Cozmo", y = 6, image = "cozmo.png"),
            aes(x = x, y = y, image = image, size = 0.1), inherit.aes = FALSE) +
  geom_image(data = data.frame(x = "Zeno", y = 7.5, image = "zeno.jpg"),
            aes(x = x, y = y, image = image, size = 0.1), inherit.aes = FALSE) +
  geom_image(data = data.frame(x = "Robovie", y = 7.5, image = "robovie.png"),
            aes(x = x, y = y, image = image, size = 0.1), inherit.aes = FALSE) +
  geom_image(data = data.frame(x = "Furhat", y = 5, image = "furhat.jpg"),
            aes(x = x, y = y, image = image, size = 0.2), inherit.aes = FALSE) +
            scale_size_identity()

ggsave("robot_models.pdf", width = 15)
```

```{r}
dat_moi <- create_counts_dataframe(dat, "robot_interaction") %>%
    mutate(Var1 = dplyr::recode(Var1,
                           "real-life" = "Real Life",
                           "video" = "Reported",
                           "life-mediated" = "Live-Mediated",
                           "picture" = "Picture",
                           "virtual-agent" = "Virtual Agent",
                           "augmented-reality" = "Augmented Reality",
                           "hybrid" = "Hybrid"))
  

create_bar_graph(dat_moi, "N.R.", "grey", "Mode of Interaction", "Percentage of Total Studies (N = 325)", "Mode of Interaction")

ggsave("interaction_mode.pdf", width = 15)
```

```{r}
operation_dat <- operation_dat %>%
    mutate(Var1 = dplyr::recode(Var1,
                           "WoZ" = "Wizard of Oz",
                           "A" = "Autonomous",
                           "PS" = "Pre-scripted",
                           "TO" = "Tele-Operated",
                           "SA" = "Semi-Autonomous",
                           "mixed" = "Mixed",
                           "N.A." = "Not Applicable")) 

operation_dat <- rbind(operation_dat, new_row)
  

create_bar_graph(operation_dat, "N.R.", "grey", "Mode of Operation", "Percentage of Total Number of Studies", "Mode of Operation")

ggsave("robot_operation.pdf", width = 15)
```

### Open Science
```{r}
gg_ethics <- create_counts_dataframe(dat_pies_unique, "ethics")


colour_ethics <- c("Reported" = "#F4A582",
                   "N.A." = "#D6604D",
                   "Not Reported" = "#B2182B")

gg_ethics_p <- create_pie_chart(
  gg_ethics, 
  "Ethical Approval", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_ethics, line_width = 1, text_size = 5, plot_title = "Ethical Approval")

gg_consent <- create_counts_dataframe(dat_pies_unique, "consent")

gg_consent_p <- create_pie_chart(
  gg_consent, 
  "Informed Consent", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_mapping2, line_width = 1, text_size = 5, plot_title = "Informed Consent")


gg_open_access <- create_counts_dataframe(dat_pies_unique, "open_access")

gg_open_access$Var1 <- factor(gg_open_access$Var1, levels = c("Available", "Not Available"))

colour_access <- c("Available" = "#F4A582",
                   "Not Available" = "#B2182B")

gg_open_access_p <- create_pie_chart(
  gg_open_access, 
  "Open Access", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_access, line_width = 1, text_size = 5, plot_title = "Open Access")

gg_prereg <- create_counts_dataframe(dat_pies_unique, "prereg") %>%
  mutate(Var1 = factor(Var1, (levels = c("Pre-Registered", "Not Pre-Registered"))))

colour_prereg <- c("Pre-Registered" = "#F4A582",
                   "Not Pre-Registered" = "#B2182B")

gg_prereg_p <- create_pie_chart(
  gg_prereg, 
  "Pre-Registration", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_prereg, line_width = 1, text_size = 5, plot_title = "Pre-Registration")

open_pies <- ggarrange(gg_ethics_p, gg_consent_p, gg_open_access_p, gg_prereg_p, ncol=2, nrow=2)

ggsave("ethics_pies.pdf", width = 20, height = 17)
```

# IN PROGRESS FUNCTION
```{r}
create_pie_chart <- function(data, legend_label, nudge_label = 1, label_spacing = 1, colour_mapping, line_width = 1, text_size = 5, plot_title = NULL, legend_order) {
  # Reorder the data based on the desired order of the legend
  data$Var1 <- factor(data$Var1, levels = legend_order)
  
  # Create a custom color palette with the specified mapping
  custom_palette <- colour_mapping[match(data$Var1, names(colour_mapping))]
  
  data <- data %>%
    arrange(desc(data$Var1)) %>%
    mutate(label_position = cumsum(percent) - percent / 2)
  
  data$label_position <- ifelse(data$label_position > 0.75, data$label_position - 1, data$label_position)
  
  ggplot(data, aes(x = 0, y = percent, fill = Var1)) +
    geom_col(width = 1) +
    coord_polar(theta = "y") +
    labs(fill = legend_label, title = plot_title) +
    scale_fill_manual(values = custom_palette) +
    geom_segment(
      aes(y = label_position, yend = label_position, x = 0.2, xend = nudge_label * (1 - label_spacing)),
      size = line_width
    ) +
    geom_text(
      aes(y = label_position, label = paste0(percent, "%")),
      nudge_x = nudge_label,
      size = text_size
    ) +
    theme_void() +
    theme(
      legend.title = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, margin = margin(b = 0))
    )
}

```


#CURRENT FUNCTION
```{r}
create_pie_chart <- function(data, legend_label, nudge_label = 1, label_spacing = 0.25, colour_mapping, line_width = 1, text_size = 5, plot_title = NULL, legend_order) {
  # Reorder the data based on the desired order of the legend
  data$Var1 <- factor(data$Var1, levels = legend_order)
  
  # Create a custom color palette with the specified mapping
  custom_palette <- colour_mapping[match(data$Var1, names(colour_mapping))]
  
  data <- data %>%
    arrange(desc(data$Var1)) %>%
    mutate(label_position = cumsum(percent) - percent / 2)
  
  data$label_position <- ifelse(data$label_position > 0.75, data$label_position - 1, data$label_position)
  
  ggplot(data, aes(x = 0, y = percent, fill = Var1)) +
    geom_col(width = 1) +
    coord_polar(theta = "y") +
    labs(fill = legend_label, title = plot_title) +
    scale_fill_manual(values = custom_palette) +
    geom_segment(
      aes(y = label_position, yend = label_position, x = 0.2, xend = nudge_label * (1 - label_spacing)),
      size = line_width
    ) +
    geom_text(
      aes(y = label_position, label = paste0(percent, "%")),
      nudge_x = nudge_label,
      size = text_size
    ) +
    theme_void() +
    theme(
      legend.title = element_text(face = "bold"),
      plot.title = element_text(hjust = 0.5, margin = margin(b = 0))
    )
}

```


```{r}
colour_open <- c("Available" = "#F4A582",
                   "Partially Available" = "#D6604D",
                 "Not Available" = "#B2182B",
                   "Not Applicable" = "#67001F",
                 "Upon Request" = "#FDDBC7")

colour_materials <- c("Available" = "#F4A582",
                   "Partially Available" = "#D6604D",
                 "Not Available" = "#B2182B")

gg_materials <- create_counts_dataframe(dat_pies_unique, "open_materials")

gg_materials_p <- create_pie_chart(
  gg_materials, 
  "Open Materials", nudge_label = 1, label_spacing = 0.25,
  line_width = 1, text_size = 5, plot_title = "Open Materials",
  colour_mapping = colour_materials)


gg_measures <- create_counts_dataframe(dat_pies_unique, "open_measures")

gg_measures_p <- create_pie_chart(
  gg_measures,
  "Open Measures",
  nudge_label = 1,
  label_spacing = 0.3,
  colour_mapping = colour_materials,
  line_width = 1,
  text_size = 5,
  plot_title = "Open Measures")


colour_code <- c("Available" = "#F4A582",
                "Partially Available" = "#D6604D",
                "Not Available" = "#B2182B",
                "Not Applicable" = "#67001F")

gg_code <- create_counts_dataframe(dat_pies_unique, "open_code")

gg_code_p <- create_pie_chart(
  gg_code, 
  "Open Code", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_code, line_width = 1, text_size = 5, plot_title = "Open Code")

gg_data <- create_counts_dataframe(dat_pies_unique, "open_data")
gg_data_p <- create_pie_chart(
  gg_data, 
  "Open Data", nudge_label = 1, label_spacing = 0.25,
  colour_mapping = colour_open, line_width = 1, text_size = 5, plot_title = "Open Data")

open_pies <- ggarrange(gg_materials_p, gg_measures_p, gg_code_p, gg_data_p)

open_pies

ggsave("open_pies.pdf", width = 20, height = 17)
```












